\documentclass{cover-letter-class}

% Set geometry
\setlength\highlightwidth{8cm}
\setlength\headerheight{3cm}
\setlength\marginleft{1cm}
\setlength\marginright{\marginleft}
\setlength\margintop{1cm}
\setlength\marginbottom{1cm}

% Fonts
\RequirePackage{fontspec}
\setmainfont{Carlito}

% Colors
\definecolor{headerfontcolor}{HTML}{000000}
\definecolor{red}{HTML}{FF0000}

\usepackage{setspace}

% Set document
\begin{document}

\name{Justin Napolitano}
\jobtitle{Strategist}
\contactinfo{\email{personal.jnapolitano@gmail.com} \phone{832-446-8685} \linkedin{linkedin.com/in/justin-napolitano}{https://www.linkedin.com/in/justin-napolitano} \github{github.com/justin-napolitano}{https://github.com/justin-napolitano}}
% \photo[round]{head_shot.jpeg}{4cm}

% Call the aligned header with the desired alignment
\alignedheader[round]{center} % Use 'left', 'right', or 'center'


% Double spacing
\doublespacing
% Main Body
\mainbody{
    % \section*{Cover Letter}
    
    \begin{flushleft}
        \textbf{Harris for President,} \\
        % 620 8th Avenue \\
        % New York, NY 10018 \\
        % USA \\
        % 212-556-1234
    \end{flushleft}
    
    \vspace{1em}
    
    \noindent

    \raggedright

    I am writing to apply for the Analytics Engineer position for the next President of the United States.

    \vspace{1em}


    I want to begin this letter by stating that I believe in upholding rigor, acting according to principle, and ensuring impartial analysis backed by valid data. 

    \vspace{1em}

    My first professional role was as a Research Assistant at the University of Central Florida. I collaborated with Dr. Demet Mousseau to develop an event-level database of human rights violations committed by any actor of the Turkish-Kurdish Conflict. My role required that I build a matrix of human rights law provisions to enable a rotating team of research assistants to accurately and impartially code violations. I systematized the data verification procedures and scripted the data cleaning methodology. I have had a passion to produce work to progress social initiatives that I care about that has since been unfulfilled.  

    \vspace{1em}

    In my most recent role as a media strategist and analytics engineer at Penske Media Corporation, I developed comprehensive reporting infrastructure for the audience marketing, subscription, editorial, and SEO teams. I focused on integrating massive amounts of data into pragmatic reporting solutions. I met daily with core stakeholders to strategically guide responses to audience signals uncovered within our data streams.  
    
    \vspace{1em}

    I am most familiar with GCP, but I have also built comprehensive solutions in Azure and AWS. I am proficient in SQL dialects unique to BigQuery, Snowflake, MySQL, and PostgreSQL. I know Python and Julia well enough to clean and analyze data at scale. I can also work with SAS and SPSS statistical software.  
    
    \vspace{1em}
    That said, data and tech are tools that inform decision-making and reduce operational friction. Valid analysis requires rigorous planning and a commitment to impartiality. Ultimately, research initiatives succeed when data professionals surrender themselves to transparency and neutrality. I am dedicated to upholding this standard. I believe I will be an asset to the Harris Campaign. I want to contribute to the betterment of my country. Please consider my application.

    % Regardless, I believe data and tech are tools that inform and reduce operational friction. Valid analysis—driven by accurate data and rigorous planning—is only one component of a successful business strategy. Ultimately, the practitioners enable an initiative to succeed. Journalists, data scientists, and IT staff must all be capable and willing to align with business goals.

    
    \vspace{1em}
    

    % I value establishing strong relationships with stakeholders based on mutual respect. Every new initiative should be evaluated for its impact on newsroom staff. I prioritize maintaining effective processes over adopting new technologies for their own sake. Every voice matters, and each person contributes to the success of strategic goals.

    
    \vspace{1em}

    % In all my work, I am guided by a commitment to integrity and the value of independent thought. As a research assistant, I led data teams to investigate the impact of war and oppression as truthfully as possible. It is painful, but it is important to detail the reality of the lives of people bound by circumstances beyond their control. Dr. Attar's video—recently published by The Times—explicitly showing the human toll in Gaza shook me to my core. I believe this is the role of journalism and The New York Times. I want to be a part of it.

    \vspace{1em}

    \noindent
    Sincerely,

    \vspace{1em}

    \noindent
    Justin Napolitano
}



\end{document}


   